\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\bfseries\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Bhavish Kumar} \\ \vspace{1pt}
    \small 0330-2341348 $|$ \href{mailto:Bhavishsindhi3@gmail.com}{\underline{Bhavishsindhi3@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/bhavish-kumar511}{\underline{www.linkedin.com/in/bhavish-kumar511}} $|$
    \href{https://github.com/bhavish511}{\underline{github.com/bhavish511}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fast National University}{Karachi, Sindh}
      {Bachelor in Computer Science }{2021 -- Present}
  \resumeSubHeadingListEnd
  
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, SQL, NoSQL, JavaScript, HTML/CSS} \\
     \textbf{Developer Tools}{: Git/Git-Lab, VS Code, PyCharm} \\
     \textbf{Frameworks \& Libraries}{: Node.js, Express.js, Pandas, NumPy, Matplotlib, scikit-learn, scikit-image, Pytorch/Keras}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
       \resumeProjectHeading
	{\textbf{Predictive Modeling for Agriculture,  ML-Model} \\ 
	\emph{Python, pandas, Matplotlib, scikit-learn}}{Aug 2024}
          \resumeItemListStart
            \resumeItem{Developed a logistic regression model to predict crop types using soil metrics such as nitrogen, phosphorous, potassium, and pH.}
            \resumeItem{Preprocessed data, evaluated feature performance with F1-scores, identified potassium as the most predictive feature, and created visualizations to present results.}
          \resumeItemListEnd
       \resumeProjectHeading
	{\textbf{Text Classification and Clustering using Vector Space Model Information Retrieval} \\ 
	\emph{Python, Numpy, Matplotlib, scikit-learn}}{April 2024 -- May 2024}
          \resumeItemListStart
            \resumeItem{Implemented KNN and K-Means for text classification and text clustering respectively on 20 raw text documents}
            \resumeItem{Achieved a precision rate of over 90\% and a recall rate of 80\% in predictive modeling}
          \resumeItemListEnd
	  \resumeProjectHeading
	{\textbf{Weather Web App} $|$ \emph{Node.js, Express.js, MySQL, Handlebars, CSS}}{June 2023 -- July 2023}
          \resumeItemListStart
            \resumeItem{Developed a web application that provides real-time weather data based on user-input city names.}
            \resumeItem{Utilized Node.js and Express.js for backend infrastructure, handling HTTP requests, routing, and middleware.}
            \resumeItem{Integrated external APIs to retrieve and display up-to-date weather conditions, including temperature, humidity, and forecasts.}
          \resumeItemListEnd
       \resumeProjectHeading
          {\textbf{Downy Shoes Wear Web App} $|$ \emph{Node.js, Express.js, MySQL, Handlebars, CSS}}{Nov 2023 -- Dec 2023}
          \resumeItemListStart
            \resumeItem{Developed e-commerce web with user, admin features product browsing, cart manage, and secure transactions.}
            \resumeItem{Built an admin dashboard for inventory management, product updates, and viewing user purchases.}
            \resumeItem{Integrated Handlebars for dynamic content generation, MySQL for data management, ensuring efficient operations and data integrity.}
          \resumeItemListEnd
       \resumeProjectHeading
          {\textbf{Car Rental System} $|$ \emph{C++}}{April 2022 -- May 2022}
          \resumeItemListStart
            \resumeItem{I employed OOP principles and C++ programming to create a user-friendly terminal-based Car Rental System.}
            \resumeItem{The system uses file handling for data storage and includes client and admin functionalities, plus a login system.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CodSoft}{Dec 2023}
      {Web Development Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Developed a Tic Tac Toe game with a console-based interface, implement both two-player and one-player functionality.}
        \resumeItem{Created a "Guess the Number" game, utilizing random number generation and user input handling.}
        \resumeItem{Built feature-rich to-do list app for task management, data structures like vectors to enhance user experience.}
      \resumeItemListEnd
%-----------Certifications-----------
\section{Certifications}
      \resumeItemListStart
        \resumeItem{Python Toolbox -DataCamp}
        \resumeItem{Data Manipulation in Pandas Toolbox -DataCamp}
        \resumeItem{Image Processing in Python -DataCamp}
        \resumeItem{Supervised Learning with scikit-learn -DataCamp}
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
